---
title: "Maslow exploration"
author: "Russell Goldenberg"
date: "Last updated: `r format(Sys.time(), '%B %d, %Y')`"
output: 
  puddingR::puddingTheme:
    toc: true
    code_folding: "show"
    number_sections: "false"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Kiki, do you love me? Are you riding?  
Say you'll never ever leave from beside me  
'Cause **I want ya**, and **I need ya**  
And I'm down for you always  

Drake obviously has a lot of needs and wants. Some things to explore...

* What are the 5 levels of needs of musicians?
* where do the needs fall in the actual Maslow's hierarchy?
* straight up wants vs. needs comparison
* who are the neediest artists? *requires full artist discog
* what are the misclassified needs that are really wants?

### Load Packages

```{r load_packages, message = FALSE, warning = FALSE}
# For general data cleaning and analysis
library(tidyverse)

# If your data includes dates that need to be wrangled
library(lubridate)

# For keeping your files in relative directories
library(here)

# For interactive/searchable tables in your report
library(DT)
```

```{r load_data}
filepath_meta <- here::here("assets", "data", "raw_data", "song_metadata.csv")
song_data <- read_csv(filepath_meta)
artist_data <- song_data %>% group_by(artist)

# reduce artists to just those with 1+ solo billboard appearances
artist_vetted <- artist_data %>%
  summarize(count=n()) %>%
  arrange(desc(count)) %>%
  filter(count >= 1)

# reduce songs to reduced artists
song_vetted <- song_data %>% filter(artist %in% artist_vetted$artist)
```

## Data Analysis

```{r parse_lyrics}
dir_in <- here::here("assets", "data", "raw_data", "lyrics")
file_out <- here::here("assets", "data", "processed_data", "needs_wants.csv")

# loop through each song file and find wants and needs
data_needs_wants <- pmap_df(song_vetted, function(...) {
  argv <- c(...)
  filepath <- paste(dir_in, argv["fname"], sep="/")
  lines <- read_lines(filepath)
  
  # convert vector to dataframe
  data <- as.data.frame(lines) %>%
    # filter to lines with text
    filter(lines != "") %>% 
    # get rid of duplicate lines
    unique() %>% 
    # lowercase all text
    mutate(lines=str_to_lower(lines)) %>%
    # reduce to lines with desired verbage
    filter(str_detect(lines, "i need ") | str_detect(lines, "i want ")) %>%
    # add in artist name column + title
    mutate(artist=argv["artist"], title=argv["title"])
})

write.table(data_needs_wants, file = file_out, row.names = FALSE, sep = ",")
```

Sweet. Let's checkout out some of the preliminary results, just looking at solo artists (no features) where a line includes an **I need** or **I want** expression.

```{r results}
datatable(data_needs_wants, rownames = FALSE, filter = "top", options = list(pageLength = 20, scrollX = TRUE))
```

### What are the 5 levels of needs of musicians?
```{r levels}
data_needs <- data_needs_wants %>% filter(str_detect(lines, "i need "))
```

```{r results_needs}
datatable(data_needs, rownames = FALSE, filter = "top", options = list(pageLength = 20, scrollX = TRUE))
```
